\documentclass[10pt]{extarticle}
%\documentclass[]{file}
\usepackage[margin=0.2in]{geometry}
\usepackage{romannum}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{multicol}
\setlist[itemize]{noitemsep, topsep=0pt}
\addtolength{\parskip}{-1.5mm}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!50,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
    boxsep=3pt,
    arc=0pt,outer arc=0pt,
    }
\begin{document}
\begin{flushleft}
\noindent {\huge\textbf{Jinit Shah}}
\end{flushleft}
9416, 4th Place  \hfill\textbf{Email : }hellojinit@gmail.com
\\Lorton, VA \hfill\textbf{Website : } \href{https://www.jinitshah.com}{jinitshah.com}
\vspace{-6pt}
\\
\noindent\rule[0.5ex]{\linewidth}{1pt}
\medskip
{\large \textbf{\begin{tcolorbox}\textsc{ EDUCATION}\end{tcolorbox}}}
\begin{itemize}
    \item \textbf{Virginia Tech}, Blacksburg, VA \hfill\hfill(\textit{Exp. Graduation: Spring 2023})
    \begin{itemize}
        \item B.S. in Computer Science 
        \item B.S. in Applied Discrete Mathematics
        \item Loves data, ML and its power to help make world a better place - Advocate for individual data ownership and privacy
    \end{itemize}
\end{itemize}

{\large \textbf{\begin{tcolorbox}\textsc{ WORK EXPERIENCE}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Machine Learning Intern} \hfill\hfill(\textit{May 2022 - July 2022})\\\textbf{Ventera Corporation}, Reston, VA 
\begin{itemize}
\item Created and developed \textbf{recommendation machine learning models} for a web application that helps users picks restaurants.    
\item Helped design and develop a full stack web application using MEAN stack and \textbf{agile workflow}. 
\item Worked on creating guidelines and pillars for \textbf{human-centered AI} and the ethics & biases related to that.
\end{itemize}

\item \textbf{Software Intern} \hfill\hfill(\textit{Nov 2020 - May 2021})\\\textbf{Deep Cognition}, Remote
\begin{itemize}
\item Developed \textbf{CNN and RNN machine learning models} and created tutorials about Deep Learning Studio. 
\end{itemize}
\item \textbf{IT Intern} \hfill\hfill(\textit{Summer 2017, 2018, 2019, 2020})\\\textbf{Linc Solutions Inc.}, Lorton, VA
\begin{itemize}
\item Hardware and networking, Software installation and configuration, System update.
\item Troubleshot and fixed wide variety of broken electronics including laptops, tablets, desktops, switches etc.
\end{itemize}
\item \textbf{IT Intern \& Assistant Chemist Intern}\hfill\hfill(\textit{Winter 2018, 19, 20})\\\textbf{Garfin India Inc}, Gandhinagar, India
\begin{itemize}
\item Researched and headed the meetings with contracting companies to rebuilt web presence of the company for their future IPO plans.
\item Restructured the entire IT platform: implemented various softwares like CRM, Collibra and migrated data from on premise servers to AWS cloud.
\end{itemize}
\end{itemize}
\vspace{1mm}
\medskip
%\newpage
%\end{itemize}
{\large \textbf{\begin{tcolorbox}\textsc{ EXTRA-CURRICULAR ACTIVITIES}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Co-President} of \textbf{Artificial Intelligence \& Machine Learning Club at VT} where my team and I managed and exponentially grew the club (550+ members). \hfill\hfill\textit{(Spring 2021 - Present)}
\begin{itemize}
    \item Co-hosted \textbf{AWS Deep Racer} Competition with \textbf{Peraton}.
    \item Gave lectures on various ML models with hands-on coding tutorials to club members and worked on innovative ML projects 
    \item Sat on \textbf{CS Dean Student Advisory} meetings to provide students' perspectives to help improve the CS program. 
\end{itemize} 
\item \textbf{PR Officer} for \textbf{Council of International Student Organization(CISO)}, an umbrella organization representing all international student organizations.\hspace{335}\textit{(August 2020 - Present)}
\begin{itemize}
    \item Created and implemented marketing plans for Rubber Ducky race, International Street Fair, Dance of Nations etc.
    \item Represented CISO on \textbf{VT's SBB} (Student Budget Board) - the committee that allocate funds to student organizations. 
\end{itemize}
\item \textbf{President of Vawter Hall}: Elected as the President of on-campus dorm at VT to help improve student life.\hfill\hfill\textit{(2019-2020)}
\end{itemize}
\vspace{-2mm}
%\medskip
%{\large \textbf{\begin{tcolorbox}\textsc{Other Projects}\end{tcolorbox}}}
%\begin{itemize}
%\end{itemize}
\medskip
\vspace{2mm}
{\large \textbf{\begin{tcolorbox}\textsc{ PERSONAL PROJECTS}\end{tcolorbox}}}
\begin{itemize}
\itemsep0em
\item \textbf{Founder, }\textbf{Handsway App}. \hfill\hfill \textit{(Launched Feb 2022)}
\begin{itemize}
\item \textit{Handsway} (\textbf{\href{https://www.renee.app/handsway}{renee.app/handsway}}) is a one-of-kind, completely free, iOS application that uses machine learning to translate American Sign Language signs to text in real time.  
\item More than 500k+ people in rely on ASL in US \& Canada. This app helps break the barrier between them and people who don't understand ASL. 
\end{itemize}
\item \textbf{Founder, }\textbf{Renee} \hfill\hfill \textit{(Launched Jan 2022)}
\begin{itemize}
\item Non-profit company that uses the power of technology to create free-to-use applications that help make world more accessible like: Handsway and Renee App(Social Media that cares about its users privacy, mental health and safety).
\end{itemize}
\end{itemize}
\medskip
{\large \textbf{\begin{tcolorbox}\textsc{ TECHNICAL SKILLS}\end{tcolorbox}}}
\begin{itemize}
\itemsep0em
\item \textbf{Programming Languages:} Python, JavaScript, Typescript, JAVA, C++, C,  Mathematica, MATLAB, Swift
\item \textbf{Softwares/Libraries/Frameworks:} NumPy, Scikit-learn, Express, NodeJS, XCode, Orange, Anaconda, MS Office Suite, Logger Pro, Firebase, Git, MySQL, MongoDB
\item \textbf{Certifications: Neural Network and Deep Learning }- Coursera (Credential ID: SX68G6SK9UJ4)
\item \textbf{Websites: }\href{https://www.jinitshah.com}{jinitshah.com}, \href{https://www.github.com/hellojinit}{github.com/hellojinit}, \href{https://www.linkedin.com/in/hellojinit}{linkedin.com/in/hellojinit}
\end{itemize}

\end{document}
